---
title       : Developing Data Products
subtitle    : Final Project, 2015
author      : Eladio Montero
job         : Data Analyst
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
url:
  lib: ./libraries
  assets: ./assets
--- .slides

## The Shiny App.

### Summary:

1. The project.
2. The Explanation
3. R Code Examples

--- .slides
## The Project

The project was made for the Last Course of the Data Science Specialization for Coursera.
The guide for this course is Brian Caffo.
The purpose of this project is to develop a data product, like we are going to do in the real life. All without the web development expertise.

The Project Consist of two parts: The Hours Calculator for the Data Science Specialization.
The other part is an age calculator in terms of days, hours, minutes and seconds.

--- .slides

## The Explanation.

Next, we are going to explain each part separately:

1. First Part:

Since all the courses in the Specialization take on average 4 weeks to complete, the calculation is just the courses times the hours spent times 4. So this gives you how many hours have you spent on this site learning.

```{r}

input1 = 4 #This is the value for the courses taken.
input2 = 6 #This is the value for the average hours per week
print(input1 * 4 * input2)

```



--- .slides

### The Explanation. (Continued)

2. Second Part:

With the function datediff, I can calculate in terms of units (days, hours, minutes or seconds) how much has passed since a specified date. It is impressive how much seconds I've lived! I took advantage of the function difftime, which gives me the difference between two dates, in terms of days, hours, minutes and seconds.

```{r}
date1 = as.Date("1990/06/25") #My Birthday
date2 = Sys.Date() # The system date, as for today.
print(as.numeric(difftime(date2, date1, units = "secs")))

```


